Thesis outline

### 2017-06-10 KellyDouglass/Thesis/Thesis_sections/Introduction.tex
Finished writing intro

% What do we already know about the environmental influence?

% Dwarf galaxies

\begin{figure}
    \includegraphics[width=0.65\textwidth]{Images/Intro/1sig_13-23_SDSS_Mr_hist_count_fill}
    \caption[Absolute magnitude distribution of galaxies in SDSS DR7]{Absolute 
    magnitude ($M_r$) distribution of galaxies in SDSS DR7, separated into void 
    and wall environments.  Dwarf galaxies are defined as galaxies with absolute 
    magnitudes fainter than -17 ($M_r > -17$).  For reference, the Milky Way has 
    an absolute magnitude $M_r \approx -20$.}
\end{figure}

% Galaxy structure

@@

\begin{figure}
    \includegraphics[width=0.9\textwidth]{Images/Intro/Kirchoff}
    \caption[Kirchoff's laws of spectroscopy]{Three different viewpoints of the 
    light emitted from a star and/or a cool cloud of gas, representing 
    Kirchoff's laws of spectroscopy.  A star emits light across all wavelengths, 
    so the resulting spectrum is known as a continuous spectrum.  Star's light 
    that has passed through a cloud of cool gas before being observed is an 
    absorption spectrum, where the elements in the cloud have absorbed some of 
    the light at specific wavelengths (corresponding to the particular elements 
    present in the gas).  If observed off the line-of-sight of the star, the 
    light emitted from the cloud of cooler gas is named an emission spectrum, 
    where the gas is re-radiating the light it absorbed from the star.}
\end{figure}

\begin{figure}
%    \includegraphics[width=0.9\textwidth]{Images/Intro/spectrum}
    \caption[Sample (void) dwarf galaxy spectrum]{Example SDSS DR7 spectrum --- 
    this is a void dwarf galaxy whose gas-phase chemical abundances are slightly 
    above average.  The [\ion{O}{3}] $\lambda$4363 auroral line is circled in 
    red, while the [\ion{O}{3}] $\lambda \lambda$4959,5007 doublet is circled in 
    yellow.}
\end{figure}

% Outline of Thesis
% Pose the problem - how does the large-scale environment affect galaxy evolution?
We want to understand how dark matter affects the evolution of a galaxy, and 
what influence it has on a galaxy's star formation.  To do this, we compare the 
properties of galaxies living in voids with galaxies in denser regions in an 
effort to understand how the properties of the gas and the history of star 
formation in a galaxy depend on the environment.  We then try to infer what 
these results tell us about the dark matter structure and history of the galaxy.

>>>>

% What do we already know about the environmental influence?
Observational studies of void galaxies have included investigation of 
photometric properties such as luminosity \citep{Hoyle05,Croton05,Moorman15}, 
color and morphological type \citep{Grogin00,Rojas04,Patiri06,Park07,
vonBendaBeckmann08,Hoyle12}, star formation rates estimated from optical 
spectroscopy and UV photometry \citep{Rojas05,Moorman15,Beygu16}, and gas 
content \citep{Kreckel12,Moorman16,Jones16}.  When compared to galaxies in 
denser regions, void galaxies are fainter, of late morphological types, bluer, 
forming stars at higher rates per unit stellar mass, and more gas rich.

% Dwarf galaxies
\begin{figure}
    \includegraphics[width=0.65\textwidth]{Images/Intro/1sig_13-23_SDSS_Mr_hist_count_fill}
    \caption[Absolute magnitude distribution of galaxies in SDSS DR7]{Absolute 
    magnitude ($M_r$) distribution of galaxies in SDSS DR7, separated into void 
    and wall environments.  Dwarf galaxies are defined as galaxies with absolute 
    magnitudes fainter than -17 ($M_r > -17$).  For reference, the Milky Way has 
    an absolute magnitude $M_r \approx -20$.}
\end{figure}

In particular, we are going to study the effects of the large-scale environment 
on the formation and evolution of dwarf galaxies.  Defined to be galaxies with 
absolute magnitudes fainter than -17 ($M_r > -17$), the lower stellar masses of 
these systems correspond to more shallow gravitational potential wells.  This 
causes any environmental effects to have a more significant influence on dwarf 
galaxies than on galaxies with larger stellar masses.  In addition, studying 
void dwarf galaxies will complement previous studies of dwarfs in groups and 
clusters because the assembly histories of low-mass galaxies are predicted to 
be very different \citep[e.g.,][]{Gao07,Lackner12}.  Observations to date also 
show that the properties of dwarf galaxies vary dramatically with the 
environment \citep[e.g.,][]{Ann08,Geha12}.

@@

The first stars that formed are thought to have been composed of only hydrogen 
(and maybe some trace amount of helium).  As stars burn, nucleosythesis creates 
heavier elements at the core.  When the stars die and expel some or all of their 
contents, the heavier elements are distributed between the surrounding 
interstellar gas and the surrounding circumgalactic medium.  When new stars form 
from this gas, they include both hydrogen and some of the heavier elements.  By 
measuring the fraction of elements heavier than helium (``metals'') relative to 
the hydrogen content (the metallicity), we measure the integrated star formation 
history of the galaxy.

\begin{figure}
    \includegraphics[width=0.9\textwidth]{Images/Intro/Kirchoff}
    \caption[Kirchoff's laws of spectroscopy]{Three different viewpoints of the 
    light emitted from a star and/or a cool cloud of gas, representing 
    Kirchoff's laws of spectroscopy.  A star emits light across all wavelengths, 
    so the resulting spectrum is known as a continuous spectrum.  Star's light 
    that has passed through a cloud of cool gas before being observed is an 
    absorption spectrum, where the elements in the cloud have absorbed some of 
    the light at specific wavelengths (corresponding to the particular elements 
    present in the gas).  If observed off the line-of-sight of the star, the 
    light emitted from the cloud of cooler gas is named an emission spectrum, 
    where the gas is re-radiating the light it absorbed from the star.}
    \label{fig:Kirchoff}
\end{figure}

We use a galaxy's spectrum to measure various properties of the stellar 
population and interstellar medium.  A galaxy's spectrum is a superposition of 
light from the stars and emission lines from the gas.  Depending on our 
viewpoint of the galaxy's light, we will see a different type of spectrum.  As 
shown in Fig. \ref{fig:Kirchoff}, if we separate a star's light by its 
wavelength, we will observe a continuous spectrum, since it is a blackbody.  If 
instead we observe the starlight after it has passed through a cloud of cooler 
gas, we will measure an absorption line spectrum; the elements in the gas cloud 
have absorbed some of the star's light at specific wavelengths corresponding to 
the particular ions present.  Finally, if we only observe the light emitted from 
the cool gas cloud, we will measure an emission line spectrum.  The method we 
employ to estimate the metallicity of a galaxy requires particular emission 
lines.  We study the gas-phase chemical abundances of \ion{H}{2} regions in a 
galaxy, where the light is coming from low-density gas partially ionized by UV 
photons emitted from young, hot stars.  Therefore, we are measuring the 
abundances of the elements produced in previous generations of stars.

\begin{figure}
%    \includegraphics[width=0.9\textwidth]{Images/Intro/spectrum}
    \caption[Sample (void) dwarf galaxy spectrum]{Example SDSS DR7 spectrum --- 
    this is a void dwarf galaxy whose gas-phase chemical abundances are slightly 
    above average.  The [\ion{O}{3}] $\lambda$4363 auroral line is circled in 
    red, while the [\ion{O}{3}] $\lambda \lambda$4959,5007 doublet is circled in 
    yellow.}
    \label{fig:spectrum}
\end{figure}

The ion transitions observed in the optical part of the spectrum (which is where 
SDSS DR7 operates) consist of forbidden transitions.  As explained in detail in 
Section \ref{sec:physics}, forbidden transitions have much longer lifetimes than 
the allowed electron transitions.  These transitions depend strongly on the 
temperature and density of the electron gas, because the long lifetimes allow 
the atoms to easily collisionally de-excite.  By taking the ratio of the 
[\ion{O}{3}] $\lambda$4363 auroral line to the [\ion{O}{3}] 
$\lambda \lambda$4959,5007 doublet, we can get an estimate of the temperature of 
the gas.  These lines are highlighted on the example SDSS DR7 spectrum shown in 
Fig. \ref{fig:spectrum}.

Oxygen is used as a proxy to measure the metallicity of an \ion{H}{2} region, 
because oxygen is the most abundant element in the universe after hydrogen and 
helium.  It also has strong emission lines in the visible wavelength range, so 
it is relatively easy to observe.  Oxygen emission is the most effective cooling 
source in an \ion{H}{2} region, so lower metallicities correspond to higher 
temperatures.  There are three main factors which determine the strength of an 
emission line: the temperature, density, and number of ions in the gas.  It is 
possible to calculate the number ratios for any of the heavy elements with 
respect to hydrogen once the electron temperature and density of the 
interstellar gas are estimated.

% Outline of Thesis
% Pose the problem - how does the large-scale environment affect galaxy evolution?
We want to understand how dark matter affects the evolution of a galaxy, and 
what influence it has on a galaxy's star formation.  To do this, we compare the 
properties of galaxies living in voids with galaxies in denser regions in an 
effort to understand how the properties of the gas and the history of star 
formation in a galaxy depend on the environment.  We then try to infer what 
these results tell us about the dark matter structure and history of the galaxy.  
In Chapter \ref{ch:Paper1}, we calculate and compare the metallicity of 135 
star-forming dwarf galaxies as a function of their large-scale environment.  We 
continue studying this galaxy sample in Chapter \ref{ch:Paper2} by estimating 
their ratios of nitrogen to oxygen and looking at how that depends on the 
large-scale environment.  To expand our dwarf galaxy sample, we derive an 
approximation for the amount of singly-ionized oxygen and repeat our analysis of 
the large-scale environmental influence on the gas-phase chemical abundances of 
1920 star-forming dwarf galaxies in Chapter \ref{ch:Paper3}.  In Chapter 
\ref{ch:smallScaleEnvironment}, we investigate how the dwarf galaxies' 
properties depend on the galaxies' distances to the nearest neighbors and 
groups.  Finally, in an effort to better understand how galaxies evolve from 
blue, star-forming systems to ``red and dead,'' we discover a way to classify 
galaxies into their location on the color-magnitude diagram in Chapter 
\ref{ch:GV}.

### 2017-06-10 KellyDouglass/Thesis/Thesis_sections/Paper1.tex
Finished writing intro

\chapter[Metallicity of dwarf galaxies]{Determining the large-scale environmental dependence of gas-phase metallicity in dwarf galaxies}

@@

Observational studies of void galaxies have included examination of photometric 
properties such as luminosity \citep{Hoyle05, Croton05, Moorman15}, color and 
morphological type \citep{Grogin00, Rojas04, Patiri06, Park07, 
vonBendaBeckmann08, Hoyle12} star formation rates estimated from optical 
spectroscopy and UV photometry \citep{Rojas05, Moorman15, Beygu16}, and gas 
content \citep{Kreckel12, Moorman16, Jones16}.  Void galaxies tend to be of 
lower luminosity, of late morphological type, blue, have relatively high rates 
of star formation per stellar mass, and gas rich.

>>>>

\chapter[Metallicity of dwarf galaxies]{Determining the large-scale environmental dependence of gas-phase metallicity in dwarf galaxies}\label{ch:Paper1}

@@

Observational studies of void galaxies have included examination of photometric 
properties such as luminosity \citep{Hoyle05, Croton05, Moorman15}, color and 
morphological type \citep{Grogin00, Rojas04, Patiri06, Park07, 
vonBendaBeckmann08, Hoyle12}, star formation rates estimated from optical 
spectroscopy and UV photometry \citep{Rojas05, Moorman15, Beygu16}, and gas 
content \citep{Kreckel12, Moorman16, Jones16}.  Void galaxies tend to be of 
lower luminosity, of late morphological type, blue, have relatively high rates 
of star formation per stellar mass, and gas rich.

### 2017-06-10 KellyDouglass/Thesis/Thesis_sections/Paper2.tex
Finished writing intro

\chapter[N/O ratio in dwarf galaxies]{Large-scale environmental dependence of the abundance ratio of nitrogen to oxygen in blue, star-forming galaxies fainter than $L_*$}

>>>>

\chapter[N/O ratio in dwarf galaxies]{Large-scale environmental dependence of the abundance ratio of nitrogen to oxygen in blue, star-forming galaxies fainter than $L_*$}\label{ch:Paper2}

### 2017-06-10 KellyDouglass/Thesis/Thesis_sections/Paper3.tex
Beginning of intro written
Finished writing intro

\chapter{Large-scale environmental dependence of chemical abundances in dwarf galaxies and implications for connecting star formation and halo mass}

>>>>

\chapter{Large-scale environmental dependence of chemical abundances in dwarf galaxies and implications for connecting star formation and halo mass}\label{ch:Paper3}

This chapter has been submitted to the \emph{Astrophysical Journal} by Kelly A. 
Douglass, Michael S. Vogeley, and Renyue Cen; it will be referenced as Douglass 
et. al (2017).
